Value-Suppressing Uncertainty Maps

### 2017-03-22 paper/template.tex
Added amsmath

%MC Packages and commands
\usepackage{subcaption}
\newcommand{\todo}[1]{\textbf{\textcolor{red}{TODO: #1}}\\}

@@

In this paper, we present \textbf{Value-Suppressing Uncertainty Maps} (VSUMs) for integrating data and uncertainty information in thematic maps. VSUMs intentionally alias together data values with high uncertainty, affording greater discriminability as certainty increases. Rather than a traditional two-dimensional bivariate map, with differing outputs for each combination of data and uncertainty, VSUMs can be thought of as arcs: as uncertainty increases, values are mapped to smaller and smaller sets of outputs, culminating in a singularity where all inputs are mapped to an identical, highly uncertain mark regardless of their data value. Figure \ref{fig:example} shows an example of a VSUM, compared to a more traditional bivariate map. In this work, we describe the motivations behind the use of VSUMs, examples of their utility for decision-making under uncertainty, and assess VSUMs in a crowd-sourced experiment. Our experimental results indicate that VSUMs promote better integration between uncertainty and data: X.

>>>>

%MC Packages and commands
\usepackage{subcaption}
\usepackage{amsmath}
\newcommand{\todo}[1]{\textbf{\textcolor{red}{TODO: #1}}\\}

@@

In this paper, we present \textbf{Value-Suppressing Uncertainty Maps} (VSUMs) for integrating data and uncertainty information in thematic maps. VSUMs intentionally alias together data values with high uncertainty, affording greater discriminability as certainty increases. Rather than a traditional two-dimensional bivariate map, with differing outputs for each combination of value and uncertainty, VSUMs can be thought of as arcs: as uncertainty increases, values are mapped to smaller and smaller sets of outputs, culminating in a singularity where all inputs are mapped to an identical, highly uncertain mark regardless of their data value. Figure \ref{fig:example} shows an example of a VSUM, compared to a more traditional bivariate map. In this work, we describe the motivations behind the use of VSUMs, examples of their utility for decision-making under uncertainty, and assess VSUMs in a crowd-sourced experiment. Our experimental results indicate that VSUMs promote better integration between uncertainty and data: X.
